An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-08-28 article/article.tex
added refs.bib

\author{Vasilis Gkolemis~\orcidlink{0000-0002-2636-0245}\\ATHENA RC \And
  Michael Gutmann~\orcidlink{0000-0002-5329-9910}\\University of Edinburgh \And
  Henri Pesonen~\orcidlink{0000-0003-4500-2926}\\University of Oslo
}
\Plainauthor{Vasilis Gkolemis, Michael Gutmann, Henri Pesonen}

>>>>

\author{Vasilis Gkolemis~\orcidlink{0000-0002-2636-0245}\\ATHENA RC \And
  Michael Gutmann~\orcidlink{0000-0002-5329-9910}\\University of Edinburgh \And
  Henri Pesonen~\orcidlink{0000-0003-4500-2926}\\University of Oslo

\Plainauthor{Vasilis Gkolemis, Michael Gutmann, Henri Pesonen}
